Interval Probability for Fuzzy Quantum Theories

### 2016-06-18 prob.tex
prob.tex \section{Quantum Probability Spaces} Add a lemma...

% \makeatletter
% \newtheoremstyle{indented}
%   {3pt}% space before
%   {3pt}% space after
%   {\addtolength{\@totalleftmargin}{3.5em}
%    \addtolength{\linewidth}{-3.5em}
%    \parshape 1 3.5em \linewidth}% body font
%   {}% indent
%   {\bfseries}% header font
%   {.}% punctuation
%   {.5em}% after theorem header
%   {}% header specification (empty for default)
% \makeatother
% \theoremstyle{indented}
\theoremstyle{remark}
\newtheorem{example}{Example}
\newtheorem{definition}{Definition}
\newtheorem{cor}{Corollary}
\newcommand{\events}{\ensuremath{\mathcal{E}}}
\newcommand{\qevents}{\ensuremath{\mathcal{E}}}
\newcommand{\pmeas}{\ensuremath{\mu}}
\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\pr}[2]{\langle #1, #2 \rangle}
\newcommand{\ket}[1]{|#1\rangle}
\newcommand{\bra}[1]{\langle#1|}
\newcommand{\ip}[2]{\langle #1 | #2 \rangle}
\newcommand{\proj}[1]{|#1 \rangle\langle #1 |}
\newcommand{\ps}{\texttt{+}}
\newcommand{\ms}{\texttt{-}}
\newcommand{\poss}{{\mbox{\wesa{possible}}}}
\newcommand{\imposs}{{\mbox{\wesa{impossible}}}}
\newcommand{\likely}{{\mbox{\wesa{likely}}}}
\newcommand{\unlikely}{{\mbox{\wesa{unlikely}}}}
\newcommand{\necess}{{\mbox{\wesa{certain}}}}
\newcommand{\overflow}{{\mbox{\wesa{overflow}}}}

@@

\begin{definition}[Ideal Measurement; Complement; Commutativity;
Complete Set~\cite{Swart2013,peres1995quantum,Griffiths2003}]~ 
\begin{itemize}
\item A set of mutually orthogonal projections $P_{i}$ is called an \emph{ideal
measurement} if it is a partition of the identity, i.e.,
$\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}=\mathbb{1}$.
\item If $P$ is a projection operator, then $\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P$
is also a projection operator, called \emph{complement}. It is orthogonal to $P$, has
probability~$\mu\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathbb{R}}]{-}{}\mu\left(P\right)$, 
and corresponds to the complement event~$\Omega\backslash E$
in classical probability.
\item Projection operators $P_{1}$ and $P_{2}$ \emph{commute} if $P_{1}P_{2}=P_{2}P_{1}$.
The product of two projection operators~$P_{1}P_{2}$ is also a projection
operator if and only if they commute. This corresponds to the classical intersection
between events. 
\end{itemize}
\qed\end{definition}

@@

Moreover, the Born rule can be extended to a mixed state. Suppose
we want to prepare a quantum system. As we discussed in classical
probability, our ability of preparing a state might not be prefect.
If we want to prepare $\ket{\phi}$, we may turn out preparing a set
of state~$\ket{\phi_{j}}$ each with probability~$q_{j}$, then
the state of the system can be expressed as a density matrix~$\rho=\sum_{j}q_{j}\proj{\phi_{j}}$,
where $\sum_{j}q_{j}=1$. It is natural that the quantum probability
measure introduced by $\rho$ is the combination of $\mu_{\phi_{j}}$
with respect to probability $q_{j}$~\cite{peres1995quantum,544199,RiederSvozil2007}:
\begin{eqnarray}
\mu_{\rho}\left(E\right) & = & \Tr\left(\rho E\right)=\sum_{j=1}^{N}q_{j}\mu_{\phi_{j}}\left(E\right)\textrm{ .}\label{BornRule.mixed}
\end{eqnarray}

@@

\subsection{Quantum Interval-valued Probabilities Measures}

@@

\begin{example}{[}Quantum probability measure{]} Like in the classical
case, there are $2^{8}$ events. But as Mermin explains in a simple
example~\cite{MerminPRL1990}, here is a possible probability measure:
\[
\begin{array}{rcl}
\mathbb{P}_{xxx}(\{LLL\}) & = & \frac{1}{4}\\
\mathbb{P}_{xxx}(\{LLR\}) & = & 0\\
\mathbb{P}_{xxx}(\{LRL\}) & = & 0\\
\mathbb{P}_{xxx}(\{LRR\}) & = & \frac{1}{4}\\
\mathbb{P}_{xxx}(\{RLL\}) & = & 0\\
\mathbb{P}_{xxx}(\{RLR\}) & = & \frac{1}{4}\\
\mathbb{P}_{xxx}(\{RRL\}) & = & \frac{1}{4}\\
\mathbb{P}_{xxx}(\{RRR\}) & = & 0\\
\mathbb{P}_{xxx}(E) & = & \sum_{\omega\in E}\mathbb{P}_{xxx}(\left\{ \omega\right\} )
\end{array}
\]
In contrast with the previous classical example, the event of different
electrons are not independent. More precisely, consider the event
for each electron separately:
\begin{eqnarray*}
F_{1,L} & = & \left\{ LLL,LLR,LRL,LRR\right\} \\
F_{2,L} & = & \left\{ LLL,LLR,RLL,RLR\right\} \\
F_{3,L} & = & \left\{ LLL,LRL,RLL,RRL\right\} 
\end{eqnarray*}
They are not independent means 
\[
\mathbb{P}_{xxx}(F_{1,L}\cap F_{2,L}\cap F_{3,L})=\mathbb{P}_{xxx}(\{LLL\})=\frac{1}{4}\ne\frac{1}{8}=\mathbb{P}_{xxx}(F_{1,L})\mathbb{P}_{xxx}(F_{2,L})\mathbb{P}_{xxx}(F_{3,L})\textrm{ .}
\]

>>>>

% \makeatletter
% \newtheoremstyle{indented}
%   {3pt}% space before
%   {3pt}% space after
%   {\addtolength{\@totalleftmargin}{3.5em}
%    \addtolength{\linewidth}{-3.5em}
%    \parshape 1 3.5em \linewidth}% body font
%   {}% indent
%   {\bfseries}% header font
%   {.}% punctuation
%   {.5em}% after theorem header
%   {}% header specification (empty for default)
% \makeatother
% \theoremstyle{indented}
\theoremstyle{remark}
\newtheorem{example}{Example}
\newtheorem{definition}{Definition}
\newtheorem{cor}{Corollary}
\newtheorem{lemma}{Lemma}
\newcommand{\events}{\ensuremath{\mathcal{E}}}
\newcommand{\qevents}{\ensuremath{\mathcal{E}}}
\newcommand{\pmeas}{\ensuremath{\mu}}
\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\pr}[2]{\langle #1, #2 \rangle}
\newcommand{\ket}[1]{|#1\rangle}
\newcommand{\bra}[1]{\langle#1|}
\newcommand{\ip}[2]{\langle #1 | #2 \rangle}
\newcommand{\proj}[1]{|#1 \rangle\langle #1 |}
\newcommand{\ps}{\texttt{+}}
\newcommand{\ms}{\texttt{-}}
\newcommand{\poss}{{\mbox{\wesa{possible}}}}
\newcommand{\imposs}{{\mbox{\wesa{impossible}}}}
\newcommand{\likely}{{\mbox{\wesa{likely}}}}
\newcommand{\unlikely}{{\mbox{\wesa{unlikely}}}}
\newcommand{\necess}{{\mbox{\wesa{certain}}}}
\newcommand{\overflow}{{\mbox{\wesa{overflow}}}}

@@

\begin{definition}[Ideal Measurement; Complement; Commutativity;
Complete Set~\cite{Swart2013,peres1995quantum,Griffiths2003}]~ 
\begin{itemize}
\item A set of mutually orthogonal projections $P_{i}$ is called an \emph{ideal
measurement} if it is a partition of the identity, i.e.,
$\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}=\mathbb{1}$.
\item If $P$ is a projection operator, then $\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P$
is also a projection operator, called \emph{complement}. It is orthogonal to $P$, has
probability~$\mu\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathbb{R}}]{-}{}\mu\left(P\right)$, 
and corresponds to the complement event~$\Omega\backslash E$
in classical probability.
\item Projection operators $P_{1}$ and $P_{2}$ \emph{commute} if $P_{1}P_{2}=P_{2}P_{1}$.
The product of two projection operators~$P_{1}P_{2}$ is also a projection
operator if and only if they commute. This corresponds to the classical intersection
between events. 
\end{itemize}
\qed\end{definition}

In order to motivate the definition of quantum interval-valued probability
measures later, here is an equivalent definition of quantum probability
measures.

\begin{lemma}Given a Hilbert space $\Hilb$, a function~$\mu:\events\rightarrow[0,1]$
is a probability measure if and only if $\mu$ satisfies the following
conditions:
\begin{itemize}
\item $\mu(\mathbb{0})=0$, 
\item $\mu(\mathbb{1})=1$, 
\item $\mu\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathbb{R}}]{-}{}\mu\left(P\right)$,
and 
\item for mutually orthogonal projections $P_{i}$, we have $\mu\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i}}\mu\left(P_{i}\right)$. 
\end{itemize}
\qed\end{lemma}

@@

Moreover, the Born rule can be extended to a mixed state. Suppose
we want to prepare a quantum system. As we discussed in classical
probability, our ability of preparing a state might not be prefect.
If we want to prepare $\ket{\phi}$, we may turn out preparing a set
of state~$\ket{\phi_{j}}$ each with probability~$q_{j}$. Then,
the state of the system can be expressed as a density matrix~$\rho=\sum_{j}q_{j}\proj{\phi_{j}}$,
where $\sum_{j}q_{j}=1$. It is natural that the quantum probability
measure introduced by $\rho$ is the combination of $\mu_{\phi_{j}}$
with respect to probability $q_{j}$~\cite{peres1995quantum,544199,RiederSvozil2007}:
\begin{eqnarray}
\mu_{\rho}\left(E\right) & = & \Tr\left(\rho E\right)=\sum_{j=1}^{N}q_{j}\mu_{\phi_{j}}\left(E\right)\textrm{ .}\label{BornRule.mixed}
\end{eqnarray}

@@

\subsection{Quantum Interval-valued Probability Measures}

@@

\begin{example}[Quantum probability measure] Like in the classical
case, there are $2^{8}$ events. But as Mermin explains in a simple
example~\cite{MerminPRL1990}, here is a possible probability measure:
\[
\begin{array}{rcl}
\mathbb{P}_{xxx}(\{LLL\}) & = & \frac{1}{4}\\
\mathbb{P}_{xxx}(\{LLR\}) & = & 0\\
\mathbb{P}_{xxx}(\{LRL\}) & = & 0\\
\mathbb{P}_{xxx}(\{LRR\}) & = & \frac{1}{4}\\
\mathbb{P}_{xxx}(\{RLL\}) & = & 0\\
\mathbb{P}_{xxx}(\{RLR\}) & = & \frac{1}{4}\\
\mathbb{P}_{xxx}(\{RRL\}) & = & \frac{1}{4}\\
\mathbb{P}_{xxx}(\{RRR\}) & = & 0\\
\mathbb{P}_{xxx}(E) & = & \sum_{\omega\in E}\mathbb{P}_{xxx}(\left\{ \omega\right\} )
\end{array}
\]
In contrast with the previous classical example, the event of different
electrons are not independent. More precisely, consider the event
for each electron separately:
\begin{eqnarray*}
F_{1,L} & = & \left\{ LLL,LLR,LRL,LRR\right\} \\
F_{2,L} & = & \left\{ LLL,LLR,RLL,RLR\right\} \\
F_{3,L} & = & \left\{ LLL,LRL,RLL,RRL\right\} 
\end{eqnarray*}
They are not independent means 
\[
\mathbb{P}_{xxx}(F_{1,L}\cap F_{2,L}\cap F_{3,L})=\mathbb{P}_{xxx}(\{LLL\})=\frac{1}{4}\ne\frac{1}{8}=\mathbb{P}_{xxx}(F_{1,L})\mathbb{P}_{xxx}(F_{2,L})\mathbb{P}_{xxx}(F_{3,L})\textrm{ .}
\]
